A Phenomenological Model for the Intracluster Medium that matches X-ray and Sunyaev-Zel'dovich observations

### 2013-09-28 paper1.tex
typo corrected

%MNRAS
\title[A Phenomenological Model for the Intracluster Medium]{A Phenomenological Model for the Intracluster Medium that matches X-ray and Sunyaev-Zel'dovich observations}
\author[F. Zandanel, C. Pfrommer and F. Prada]{
Fabio Zandanel$^{1,2}$, Christoph Pfrommer$^{3}$ and Francisco Prada$^{4,5,1}$\\
$^{1}$GRAPPA Institute, University of Amsterdam, Science Park 904, 1098XH Amsterdam, Netherlands, f.zandanel@uva.nl\\
$^{2}$Instituto de Astrof\'{\i}sica de Andaluc\'{\i}a (CSIC), Glorieta de la Astronom\'{\i}a, E-18080 Granada, Spain\\
$^{3}$Heidelberg Institute for Theoretical Studies, Schloss-Wolfsbrunnenweg 35, D-69118 Heidelberg, Germany, christoph.pfrommer@h-its.org\\
$^{4}$Campus of International Excellence UAM+CSIC, Cantoblanco, E-28049 Madrid, Spain\\
$^{5}$Instituto de F\'{\i}sica Te\'orica, (UAM/CSIC), Universidad Aut\'onoma de Madrid, Cantoblanco, E-28049 Madrid, Spain}
\begin{document}

>>>>

%MNRAS
\title[A Phenomenological Model for the Intracluster Medium]{A Phenomenological Model for the Intracluster Medium that matches X-ray and Sunyaev-Zel'dovich observations}
\author[F. Zandanel, C. Pfrommer and F. Prada]{
Fabio Zandanel$^{1,2}$, Christoph Pfrommer$^{3}$ and Francisco Prada$^{4,5,2}$\\
$^{1}$GRAPPA Institute, University of Amsterdam, Science Park 904, 1098XH Amsterdam, Netherlands, f.zandanel@uva.nl\\
$^{2}$Instituto de Astrof\'{\i}sica de Andaluc\'{\i}a (CSIC), Glorieta de la Astronom\'{\i}a, E-18080 Granada, Spain\\
$^{3}$Heidelberg Institute for Theoretical Studies, Schloss-Wolfsbrunnenweg 35, D-69118 Heidelberg, Germany, christoph.pfrommer@h-its.org\\
$^{4}$Campus of International Excellence UAM+CSIC, Cantoblanco, E-28049 Madrid, Spain\\
$^{5}$Instituto de F\'{\i}sica Te\'orica, (UAM/CSIC), Universidad Aut\'onoma de Madrid, Cantoblanco, E-28049 Madrid, Spain}
\begin{document}
